### 2021-11-19 documentos/pce.tex
avanzando

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The trace preserving
property is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, this
is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local feature of quantum theory. A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto. Sin embargo esos casos no son relevantes en este contexto por supuesto}. In the other hand, a map is completely positive if
 $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}. Therefore,
complete positivity ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators, trace preserving is automatically
fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.

Quantum channels can be characterized by means of the Choi-\jami{}
isomorphism~\cite{choi,jamil}. This is, given a linear operation
$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it,
$C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
Bell state between two copies of \hilbert, is positive semi-definite if and only
if $\mcE$ is completely positive.

Quantum channels have the well-known \textit{Kraus representation} (or
operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho
K^\dagger{}_i$ in fact, a linear operation is completely positive if and only
if it has a Kraus representation [cite Kraus book] 
\flnote{
probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
$\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
}\ddnote{trabajando en ello, hacia falta edicion aqui}

@@

% In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
% 1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
% the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
% $\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pce_example}
% \end{center}
% this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
% components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
% is not completely positive and therefore is not a quantum channel. In contrast, 
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pceChannel_example01}
% \end{center}
% this other example of PCE operation that leaves invariant Pauli components 
% $r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
% is a quantum channel. 
% 
% \begin{figure} % {{{
% 	\centering
% 	\hfill \hfill
% 	\includegraphics[height=2.5cm]	{tablero_1qubit}
% 	\hfill
% 	\includegraphics[height=2.5cm]{tablero_2qubits}
% %	\hspace{1mm}
% %	\includegraphics[height=2.7cm]{rho-3q}
% 	\hfill \hfill \hfill
% 	\caption{From left to right representations of identity map
% 	(also PCE operations) of 1 and 2 qubits, respectively.}
% 	\label{fig:PCE_figs}
% \end{figure} % }}}
% 
% \begin{figure} % {{{
% 	\centering
% 	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
% 	\caption{1 qubit PCE channels. }
% 	\label{fig:1qubit_PCEChannles}
% \end{figure} % }}}

>>>>

The construction of quantum channels includes basically three ingredients:
linearity, trace preserving and complete positivity. The trace preserving
property is needed to
send convex combinations of density matrices into the convex combination of the
evolution of such density matrices, this is, let $\mcE$ such linear operation,
thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
happen to the state $\rho\in \mcS(\hilbert)$. The complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local feature of quantum theory. A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto. Sin embargo esos casos no son relevantes en este contexto por supuesto}. In the other hand, a map is completely positive if
 $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
between the system and an ancilla with Hilbert space $\hilbert_k$. This ensures that every positive semidefinite operator of any
extension of the system (where the quantum channel is now a local operation) is
mapped into positive semidefinite operators. The trace preserving is automatically
fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
where $\mcE$ acts locally, is sent to a valid density matrix, this is the
substance of complete positivity.
\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}

Quantum channels can be characterized by means of the Choi-\jami{}
isomorphism~\cite{choi,jamil}. This is, given a linear operation
$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called dynamical matrix), where
$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
Bell state between two copies of \hilbert. The map \mcE is completely positive if and only
\choi is positive-semidefinite.

Furthermore, quantum channels have the well-known \textit{Kraus representation} (or
operator-sum representation) which reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{}
\end{equation}
 in fact, a linear operation is completely positive if and only
if it has a Kraus representation [cite Kraus book] 
\flnote{
probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
$\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
}\ddnote{trabajando en ello, hacia falta edicion aqui}

@@

% In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
% 1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
% the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
% $\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pce_example}
% \end{center}
% this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
% components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
% is not completely positive and therefore is not a quantum channel. In contrast, 
% \begin{center}
% \includegraphics[width=2cm]{2qubits_pceChannel_example01}
% \end{center}
% this other example of PCE operation that leaves invariant Pauli components 
% $r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
% is a quantum channel. 
% 
%
